### 2022-12-14 README.Rmd
update to readme
readme update

The approach uses quasi-random sampling (Grafston & Tille, 2013, Foster et al., 2018) to generate a quadrature scheme for numerical approximation of a Poisson point process model (Berman & Turner 1992; Warton & Shepard 2010). Quasi-random sampling quadrature are form of spatially-balanced survey design or point stratification that aims to reduce the frequency of placing samples close to each other (relative to pseudo-random or grid designs). A quasi-random quadrature design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013, Foster et al., 2018) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007). Because the quasi-random design is not on a regular grid we use Dirichlet tessellation to generate polygons for each point in the quadrature scheme. Areal weights are then derived from these polygons.

@@

```{r fig1, fig.width=7, fig.height=4, fig.align='center', echo=TRUE}
plot(ppmdata1)
```
Once the `ppmData` object has been set up it is quiet easy to fit a point process
model in R. You can use something like `glm`, `gam` or even convert the 
`ppmData` object to work directly with `spatstat::ppm`.

Here is a brief example of how you might fit a ppm using `glm`.

@@

```{r,fig.width=6, fig.height=6, fig.cap=""}
pred <- predict(covariates,
                ft.ppm,
                type="response")
plot(pred*prod(res(pred))) # scale response by area of cell.
```

>>>>

The approach uses quasi-random sampling (Grafston & Tille, 2013, Foster et al., 2018) to generate a quadrature scheme for numerical approximation of a Poisson point process model (Berman & Turner 1992; Warton & Shepard 2010). Quasi-random sampling quadrature are a form of spatially-balanced survey design or point stratification that aims to reduce the frequency of placing samples close to each other (relative to pseudo-random or grid designs). A quasi-random quadrature design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013, Foster et al., 2018) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007). Because the quasi-random design is not on a regular grid we use Dirichlet tessellation to generate polygons for each point in the quadrature scheme. Areal weights are then derived from these polygons.

@@

```{r fig1, fig.width=7, fig.height=4, fig.align='center', echo=TRUE}
plot(ppmdata1)
```
Once the `ppmData` object has been set up it is quiet easy to fit a point process
model in R. You can use something like `glm`, `gam` or even convert the 
`ppmData` object to work directly with `spatstat::ppm`. Here is a brief example 
of how you might fit a ppm using `glm`:

@@

```{r,fig.width=6, fig.height=6, fig.cap=""}
pred <- predict(covariates,
                ft.ppm,
                type="response")
plot(pred*prod(res(pred))) # scale response by area of cell.
points(presences[!duplicated(presences),1:2],pch=16,cex=0.75,col=gray(0.2,0.75))

```
